Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2020-05-27 Manuscript/manuscript.Rmd
added to discussion

>>>>

A limitation of *preciseTAD* is that it is dependent on "ground truth" boundaries provided by a user-defined TAD(loop)-caller. Ideally we would perform simulation studies to benchmark *preciseTAD* against simulated boundaries. While there are existing methods for simulating Hi-C data sets [@forcato2017comparison; @zheng2020freehi], of which boundaries can be extracted from, to date, there are no such methods for simulating ChIP-seq data. However, given *preciseTAD* is applied on chromosome-specific sections of the linear genome, we feel that aggregating results across chromosomes provides strong empirical evidence of the superiority of *preciseTAD*. Another limitation is that *preciseTAD* does not provide hierarchical boundaries, but instead simply provides the bp coordinate that demarcates TADs(loops). Studies have shown evidence of the hierarchical nature to the 3D architecture of the human genome [@hansen2018recent; @weinreb2016identification; @fraser2015hierarchical]. In such a hierarchy, the boundaries provided by *preciseTAD* can be interpreted as the lowest level of boundaries.
